Exploring probability distributions for bivariate temporal granularities

### 2019-11-14 main.Rmd
changing structure

#### Relationships between two linear granularities and association to Periodicity

@@

@@

For mapping it in graphical elements, we need to consider all the periodic granules as similar. The formalism  is attempted through the tsibble [@Wang2019-aw] framework of organizing temporal data. Suppose we have a tsibble with a time index in one column and keys and variables in other columns, a time domain, as defined by Bettini, is essentially a mapping of the index set to the time index.

A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the time index is days, then a linear granularity might be weeks, months or years.  Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of time domain. We use modular arithmetic for manipulating the index of the periodic granularities so that they are treated as similar across the coarser granularity.

Since the assumption in [@Bettini2000-vy] is that all granularities can be generated from the bottom granularity by calendar algebraic operations - we extend this notion to relate index of the two granularities in a way, which represents the circular arrangement of time.

@@

@@

A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the time index is days, then a linear granularity might be weeks, months or years.  Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of time domain. We use modular arithmetic to define circular granularity and use the following definitions:

@@

# Computation of time granularities

An algebraic representation for time granularities, which
we call the calendar algebra. It is assumed that there exists a “bottom”
granularity known to the system. Calendar algebra operations are designed to generate
new granularities from the bottom one or recursively, from those already generated.
Thus, the relationship between the operand(s) and the resulting granularities are encoded
in the operations.

>>>>

### Relationships between two linear granularities and association to Periodicity

@@

### Computation of time granularities

Linear time granularities are computed through an algebraic representation for time granularities, which is referred to as calendar algebra[@Ning2002-tf]. It is assumed that there exists a “bottom”
granularity and Calendar algebra operations are designed to generate
new granularities from the bottom one or recursively, from those already generated.
Thus, the relationship between the operand(s) and the resulting granularities are encoded
in the operations.

@@

In a cyclic organization of time, the domain is composed of a set of recurring time values. The formalism of time granularities in cyclic arrangement is attempted through the tsibble [@Wang2019-aw] framework of organizing temporal data. Suppose we have a tsibble with a time index in one column and keys and variables in other columns, a time domain, as defined by Bettini, is essentially a mapping of the index set to the time index.

A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the time index is days, then a linear granularity might be weeks, months or years. Since time is arranged in a cyclic way typically to accomodate periodicity, we will try to formalize how periodic linear granularities can be represented in a cyclic way. Since the assumption in [@Bettini2000-vy] is that all granularities can be generated from the bottom granularity by calendar algebraic operations - we extend this notion to relate index of the two granularities in a way, which represents the circular arrangement of time using modular arithmetic.

<!-- Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of time domain. . -->

@@

The constant c(x,y) is for granularities for groups into periodically, for granualrities which group into each other in a quasi-periodic way, no such constants exist and no such close form solution can be obtained.

Some examples of circular representation of finer granularities within coarse granularities in a  periodic and quasi-periodic set up are as follows:

@@

<!-- A linear granularity is a mapping of the index set to subsets of the time domain. For example, if the time index is days, then a linear granularity might be weeks, months or years.  Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of time domain. We use modular arithmetic to define circular granularity and use the following definitions: -->

@@
